Figure two

### 2025-12-05 draftFiguretwo_Ella.Rmd
figure2 shares

@@

@@

>>>>

Redo figure 2 with the 'share of papers mentioning a topic' instead, so the percentages would go above 100% which is ok. Also for the other panels, calculate the percentages per subgroups that mention,
which will also make each 'column' going above 100%

@@

## Visualization counting the share of papers & survey items instead of the raw count for each category

```{r}

papers_long <- papers %>%
  group_by(category) %>%
  summarise(n = n_distinct(ID)) %>%
  rename(Topic = category) %>% 
  mutate(share = n / length(unique(papers$ID)))

# bar plot with counts and percentage labels
pdf("plots/Figure2_category_paper_barplot_share.pdf", width = 12, height = 10)
ggplot(papers_long, aes(y = reorder(Topic, n), x = n, fill = Topic)) +
  geom_col(color = "black") +
  geom_text(aes(label = percent(share, accuracy = 1)),
            hjust = -0.3, size = 9) +
  labs(y = NULL, x = "Number of papers covering each category") +
  scale_fill_manual(values = c(
    "Perceptions" = "#8B7B8B",
    "Behavior"    = "#EED8AE",
    "Priority"    = "#CDB5CD",
    "Policy"      = "#CD919E",
    "Health"      = "#8B475D",
    "None"        = "#F4A460")) +
  theme_minimal() +
  xlim(0, 450) +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    axis.title = element_text(size = 23)
    )
dev.off()

surveys_long <- surveys %>%
  mutate(item_id = paste0(iso3, id)) %>% 
  distinct(item_id, category) %>%     # collapse multiple rows for same ID–category pair
  count(category, name = "n") %>% 
  mutate(share = n / length(unique(paste0(surveys$iso3, surveys$id)))) %>%
  rename(Topic = category)

# bar plot with counts and percentage labels
pdf("plots/Figure2_category_survey_barplot_share.pdf", width = 12, height = 10)
ggplot(surveys_long, aes(y = reorder(Topic, n), x = n, fill = Topic)) +
  geom_col(color = "black") +
  geom_text(aes(label = percent(share, accuracy = 1)),
            hjust = -0.3, size = 9) +
  labs(y = NULL, x = "Number of survey items covering each category") +
  scale_fill_manual(values = c(
    "Perceptions" = "#8B7B8B",
    "Behavior"    = "#EED8AE",
    "Priority"    = "#CDB5CD",
    "Policy"      = "#CD919E",
    "Health"      = "#8B475D",
    "None"        = "#F4A460")) +
  xlim(0, 1250) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 22),
    axis.text.x = element_text(size = 22),
    axis.title = element_text(size = 23)
    )
dev.off()

@@

## Visualizations by income group, using share
